Getting Started with the Graded Response Model (GRM): An introduction and tutorial in R

### 2024-08-19 manuscript.qmd
Revision round 1

| Model                       | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
|-----------------|--------------------|-----------------|-----------------|
| 1-PL Model (Rasch Model)    | 1\. Estimates only item difficulties (*b*). 2. Assumes that all items have equal discrimination parameters (*a*). 3. Item and person parameters are independent.                                                                                             | Dichotomous | Correct/Incorrect (0/1) |
| 2-PL Model                  | 1\. Estimates item difficulties (*b*) and item discrimination (*a*). 2. Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary.                                                                                         | Dichotomous | Correct/Incorrect (0/1) |
| 3-PL Model                  | 1\. Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*). 2. Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses. | Dichotomous | Correct/Incorrect (0/1) |
| Graded Response Model (GRM) | 1\. Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style). 2. Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item.                                                       | Polytomous  | Ordered Categories      |

@@

The output of these codes is `r e_rel`, which is rather close to marginal reliability we estimated before. This implies that RWA scale is overall highly reliable in measuring RWA trait across all participants in the sample. Generally, reliability analysis aligns with the IPFs and IIFs we saw in the previous step, i.e., the RWA scale is highly reliable overall, but works best to measure the RWA construct across participants with RWA levels between ~2*SD* below the mean and ~3*SD* above the mean.

>>>>

| Model                       | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
|-----------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------------|-------------------------|
| 1-PL Model (Rasch Model)    | 1\. Estimates only item difficulties (*b*). 2. Assumes that all items have equal discrimination parameters (*a*). 3. Item and person parameters are independent.                                                                                             | Dichotomous | Correct/Incorrect (0/1) |
| 2-PL Model                  | 1\. Estimates item difficulties (*b*) and item discrimination (*a*). 2. Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary.                                                                                         | Dichotomous | Correct/Incorrect (0/1) |
| 3-PL Model                  | 1\. Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*). 2. Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses. | Dichotomous | Correct/Incorrect (0/1) |
| Graded Response Model (GRM) | 1\. Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style). 2. Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item.                                                       | Polytomous  | Ordered Categories      |

@@

The output of these codes is `r e_rel`, which is rather close to marginal reliability we estimated before. This implies that RWA scale is overall highly reliable in measuring RWA trait across all participants in the sample. Generally, reliability analysis aligns with the IPFs and IIFs we saw in the previous step, i.e., the RWA scale is highly reliable overall, but works best to measure the RWA construct across participants with RWA levels between \~2*SD* below the mean and \~3*SD* above the mean.
